Data Appendix

### 2023-12-01 appendix.Rmd
Onde eu descubro que tem multiclonieraridade na aostra com todo mundo e ols não é significativo

---
title: "Data Appendix"
author: "Manoel Galdino"
date: "2023-11-30"
output: 
  bookdown::pdf_document2:
    toc:false
---

@@

```{r package loads}
library(data.table)
library(here)
library(janitor)
library(lubridate)
library(readxl)
library(tidyverse)
library(gt)
library(ipeadatar)
library(rstan)
library(arm)
library(rstanarm)
library(survey)
library(broom)
library(broom.mixed)
library(MetBrewer)
library(knitr)
library(ggplot2)
library(patchwork)

@@

## R Markdown

@@

In the main analysis, we restricted the sample to municipalities in the same states where the Obra Transparente project occurred. Table \@ref(tab:basic-table-s) presents a situation similar to that of the entire country, albeit with a higher baseline (11 percentage points above the whole country).

@@

df1 <- df1 %>%
  rename(date = concluida) %>%
  mutate(date = c("May 2017", "July 2019"),
         perc = scales::percent(round(num_works/total, 2)))

df2 <- df2 %>%
  rename(date = concluida) %>%
  mutate(date = c("May 2017", "July 2019"),
         perc = scales::percent(round(num_works/total, 2)))

@@

# Imbalance

@@

imb_before_s <- obras_inicio_projeto %>%
  dplyr::filter(uf %in% c("SP", "PR", "SP", "SC", "RS", "MG")) %>%
  mutate(paralyzed = as.numeric(grepl("Paralisada", situacao)),
         execution = as.numeric(grepl("Execução", situacao)),
         percentage_executed = percentual_de_execucao) %>%
  summarise(num_works = n(),
            num_paralyzed = sum(paralyzed),
            num_execution = sum(execution),
            perc_paralyzed = num_paralyzed/num_works,
            perc_execution = num_execution/num_works,
            mean_execution = mean(percentage_executed)/100) %>%
  mutate(date = "May 2017")

imb_before <- obras_inicio_projeto %>%
  mutate(paralyzed = as.numeric(grepl("Paralisada", situacao)),
         execution = as.numeric(grepl("Execução", situacao)),
         percentage_executed = percentual_de_execucao) %>%
  summarise(num_works = n(),
            num_paralyzed = sum(paralyzed),
            num_execution = sum(execution),
            perc_paralyzed = num_paralyzed/num_works,
            perc_execution = num_execution/num_works,
            mean_execution = mean(percentage_executed)/100) %>%
  mutate(date = "May 2017")

imb_after_s <- obras_fim_seg_fase %>%
  dplyr::filter(uf %in% c("SP", "PR", "SP", "SC", "RS", "MG")) %>%
  mutate(paralyzed = as.numeric(grepl("Paralisada", situacao)),
         execution = as.numeric(grepl("Execução", situacao)),
         percentage_executed = percentual_de_execucao) %>%
  summarise(num_works = n(),
            num_paralyzed = sum(paralyzed),
            num_execution = sum(execution),
            perc_paralyzed = num_paralyzed/num_works,
            perc_execution = num_execution/num_works,
            mean_execution = mean(percentage_executed)/100) %>%
  mutate(date = "July 2019")

imb_after <- obras_fim_seg_fase %>%
  mutate(paralyzed = as.numeric(grepl("Paralisada", situacao)),
         execution = as.numeric(grepl("Execução", situacao)),
         percentage_executed = percentual_de_execucao) %>%
  summarise(num_works = n(),
            num_paralyzed = sum(paralyzed),
            num_execution = sum(execution),
            perc_paralyzed = num_paralyzed/num_works,
            perc_execution = num_execution/num_works,
            mean_execution = mean(percentage_executed)/100) %>%
  mutate(date = "July 2019")

@@

# Print the combined plots
print(combined_plots)

@@

```{r fitting bayesian model, message=FALSE, echo=FALSE, cache = TRUE}
aux_indicator_ot <- df_cidades_ot %>%
  distinct(municipio, uf) %>%
  mutate(indicator_muni_ot = 1)

@@

df_balancing_aux <- obras_inicio_projeto_ot %>%
  mutate(concluida = as.numeric(grepl("Concluída", situacao)))  %>%
  mutate(municipio1 = tolower(iconv(municipio, "UTF-8",  "ASCII//TRANSLIT"))) %>%
  inner_join(aux_muni1, by = join_by(municipio1  == name_muni1, uf == abbrev_state)) %>%
  inner_join(ipea_final, by = join_by(code_muni == tcode)) %>%
  mutate(perc_pea18 =pea18/populacao,
         log_pop = log(populacao),
         log_renda = log(rpc*populacao),
         log_rpc = log(rpc),
         tipo_do_projeto = ifelse(grepl("Bloco Estrutural" ,tipo_do_projeto),
                                  "Projeto Tipo B ou C - Bloco Estrutural", tipo_do_projeto))

df_balancing_aux1 <- df_balancing_aux %>%
  mutate(concluida_num = as.numeric(concluida))

@@

#treatment effect without replacement

set.seed(120)
reg_ps_pre <- stan_lmer(te_spec_nr, data=df_balancing_aux1, iter = 100)

## After
set.seed(120)
reg_ps_pos <- stan_lmer(te_spec_nr, data=df_balancing_aux_post_se[matches_pos$match.ind,], iter = 4000, refresh=0)

@@

b1_pre_sims <- as.matrix(reg_ps_pre, 
                     pars = "indicator_muni_ot")

# Posterior mean and SD of treatment
b1_mean_pre <- mean(b1_pre_sims) # posterior mean
b1_sd_pre <- sd(b1_pre_sims)       # posterior SD

# Posterior median and 95% credible interval
b1_quant_pre <- quantile(b1_pre_sims,   probs = c(0.025, 0.50, 0.975))

b1_quant_pre <- data.frame(t(b1_quant_pre))
names(b1_quant_pre) <- c("Q2.5", "Q50", "Q97.5")

# Combine summary statistics of posterior simulation draws
b1_df_pre_cred <- data.frame(variables = "ATT before project",
                             post_mean = b1_mean_pre,
                             post_sd = b1_sd_pre,
                             b1_quant_pre[2], 
                             b1_quant_pre[1],
                             b1_quant_pre[3])

##
# After
##
b1_sims_after <- as.matrix(reg_ps_pos, 
                     pars = "indicator_muni_ot")

# Compute mean, SD, median, and 95% credible interval of treatment

# Posterior mean and SD of treatment
b1_mean_after <- mean(b1_sims_after) # posterior mean
b1_sd_after <- sd(b1_sims_after)       # posterior SD

# Posterior median and 95% credible interval
b1_quant_after <- quantile(b1_sims_after,   probs = c(0.025, 0.50, 0.975))

b1_quant_after <- data.frame(t(b1_quant_after))
names(b1_quant_after) <- c("Q2.5", "Q50", "Q97.5")

# Combine summary statistics of posterior simulation draws
b1_df_after_cred <- data.frame(variables = "ATT After project",
                             post_mean = b1_mean_after,
                             post_sd = b1_sd_after,
                             b1_quant_after[2], 
                             b1_quant_after[1],
                             b1_quant_after[3])
b1_df <- bind_rows(b1_df_pre_cred, b1_df_after_cred)
```

@@

b1_df %>% gt() %>%
  tab_header(
    title = "Effect of local OSB social monitoring on construction delivery rates",
    subtitle = "Posterior probabilities") %>%
  cols_label(
    variables = "Variables",
    post_mean = "Mean",
    post_sd = "Sd",
    Q50 = "Median",
    Q2.5 = "2.5% CI",
    Q97.5 = "97.5% CI"
  ) %>%
  fmt_number(
    columns = c(post_mean, post_sd, Q50, Q2.5, Q97.5 ),
    decimals = 3,
    use_seps = FALSE
  ) %>%
  tab_source_note(
    source_note = "452 observations for the pre-treatment period and 320 observations for the post-treatment period, resulting from the matching procedure, and encompassing municipalities in the same states as municipalities of Obra Transparente"
  ) %>%
  tab_options(., container.width = 500, container.height =     500)
```

>>>>

---
title: "Data Appendix"
author: "Manoel Galdino"
date: "2023-11-30"
output: 
  bookdown::pdf_document2:
    figsintext : yes
---

@@

```{r package loads}
library(data.table)
library(stargazer)
library(fixest)
library(here)
library(janitor)
library(lubridate)
library(readxl)
library(tidyverse)
library(gt)
library(ipeadatar)
library(rstan)
library(arm)
library(rstanarm)
library(brms)
library(survey)
library(broom)
library(broom.mixed)
library(MetBrewer)
library(knitr)
library(ggplot2)
library(patchwork)

@@

# Appendix

@@

In the main analysis, we restricted the sample to municipalities in the same states where the Obra Transparente project occurred. The reason is that there is perfect multicolinearity between our treatment and seven other control variables (mesured at the municipality level) in the unrestricted sample (log of per capita income, school frequency, log of GDP, share of poor families, illiteracy rate, and an inequality measure).

We present simple descriptive statistics and visualizations to show that the change is similar in our outcome variable considering the restricted and unrestricted sample.

Table \@ref(tab:basic-table-s) presents a situation similar to that of the entire country, albeit with a higher baseline (11 percentage points above the whole country).

@@

df1 <- df1 %>%
  rename(date = concluida) %>%
  mutate(date = c("05-17", "07-19"),
         perc = scales::percent(round(num_works/total, 2)))

df2 <- df2 %>%
  rename(date = concluida) %>%
  mutate(date = c("05-17", "07-19"),
         perc = scales::percent(round(num_works/total, 2)))

@@

## Imbalance

@@

imb_before_s <- obras_inicio_projeto %>%
  dplyr::filter(uf %in% c("SP", "PR", "SP", "SC", "RS", "MG")) %>%
  mutate(paralyzed = as.numeric(grepl("Paralisada", situacao)),
         execution = as.numeric(grepl("Execução", situacao)),
         percentage_executed = percentual_de_execucao) %>%
  summarise(num_works = n(),
            num_paralyzed = sum(paralyzed),
            num_execution = sum(execution),
            perc_paralyzed = num_paralyzed/num_works,
            perc_execution = num_execution/num_works,
            mean_execution = mean(percentage_executed)/100) %>%
  mutate(date = "05-17")

imb_before <- obras_inicio_projeto %>%
  mutate(paralyzed = as.numeric(grepl("Paralisada", situacao)),
         execution = as.numeric(grepl("Execução", situacao)),
         percentage_executed = percentual_de_execucao) %>%
  summarise(num_works = n(),
            num_paralyzed = sum(paralyzed),
            num_execution = sum(execution),
            perc_paralyzed = num_paralyzed/num_works,
            perc_execution = num_execution/num_works,
            mean_execution = mean(percentage_executed)/100) %>%
  mutate(date = "05-17")

imb_after_s <- obras_fim_seg_fase %>%
  dplyr::filter(uf %in% c("SP", "PR", "SC", "RS", "MG")) %>%
  mutate(paralyzed = as.numeric(grepl("Paralisada", situacao)),
         execution = as.numeric(grepl("Execução", situacao)),
         percentage_executed = percentual_de_execucao) %>%
  summarise(num_works = n(),
            num_paralyzed = sum(paralyzed),
            num_execution = sum(execution),
            perc_paralyzed = num_paralyzed/num_works,
            perc_execution = num_execution/num_works,
            mean_execution = mean(percentage_executed)/100) %>%
  mutate(date = "07-19")

imb_after <- obras_fim_seg_fase %>%
  mutate(paralyzed = as.numeric(grepl("Paralisada", situacao)),
         execution = as.numeric(grepl("Execução", situacao)),
         percentage_executed = percentual_de_execucao) %>%
  summarise(num_works = n(),
            num_paralyzed = sum(paralyzed),
            num_execution = sum(execution),
            perc_paralyzed = num_paralyzed/num_works,
            perc_execution = num_execution/num_works,
            mean_execution = mean(percentage_executed)/100) %>%
  mutate(date = "07-19")

@@

# Print the combined plots
print(combined_plots)
```

@@

```{r processing reg, message=FALSE, echo=FALSE}
aux_indicator_ot <- df_cidades_ot %>%
  distinct(municipio, uf) %>%
  mutate(indicator_muni_ot = 1)

@@

df_balancing_aux <- obras_inicio_projeto_ot %>%
  mutate(concluida = as.numeric(grepl("Concluída", situacao)))  %>%
  mutate(municipio1 = tolower(iconv(municipio, "UTF-8",  "ASCII//TRANSLIT"))) %>%
  inner_join(aux_muni1, by = join_by(municipio1  == name_muni1, uf == abbrev_state)) %>%
  inner_join(ipea_final, by = join_by(code_muni == tcode)) %>%
  mutate(perc_pea18 =pea18/populacao,
         log_pop = log(populacao),
         log_renda = log(rpc*populacao),
         log_rpc = log(rpc),
         tipo_do_projeto = ifelse(grepl("Bloco Estrutural" ,tipo_do_projeto),
                                  "Projeto Tipo B ou C - Bloco Estrutural", tipo_do_projeto)) %>%
  mutate(concluida_num = as.numeric(concluida))

df_balancing_aux1 <- df_balancing_aux  %>%
  dplyr::filter(uf.x %in% c("SP", "MG", "RS", "PR", "SC"))

@@

Tables below presents results from standard, frequentist regression (ols, fixed effects, both with clustered standard errors) and Bayesian regression (linear model with varying intercept).

```{r fitting, echo=FALSE, message=FALSE, results="asis"}

# Simple linear regression
fit_ols <- feols(concluida_num ~ indicator_muni_ot + log_rpc +
                   ext_pobres + freq_escola_15_1 + analfabetismo + log_renda + p10_ricos_desigualdade + percentual_de_execucao, data = df_balancing_aux1, cluster = "code_muni" )

fit_fixed <- feols(concluida_num ~ indicator_muni_ot + log_rpc + ext_pobres + freq_escola_15_1 + analfabetismo + log_renda + p10_ricos_desigualdade + percentual_de_execucao |code_muni, data = df_balancing_aux1, cluster = "code_muni")

etable(list(fit_ols, fit_fixed), tex=TRUE)

set.seed(120)
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
# system.time(reg_ps_pre <- brm(te_spec_nr, data=df_balancing_aux1, iter = 100, cores = 4, chains = 4))
# reg_ps_pre <- stan_lmer(te_spec_nr, data=df_balancing_aux1, iter = 100)

## After
# set.seed(120)
# reg_ps_pos <- stan_lmer(te_spec_nr, data=df_balancing_aux_post_se[matches_pos$match.ind,], iter = 4000, refresh=0)

@@

# b1_pre_sims <- as.matrix(reg_ps_pre, 
#                      pars = "indicator_muni_ot")

# Posterior mean and SD of treatment
# b1_mean_pre <- mean(b1_pre_sims) # posterior mean
# b1_sd_pre <- sd(b1_pre_sims)       # posterior SD
#

# Posterior median and 95% credible interval
# b1_quant_pre <- quantile(b1_pre_sims,   probs = c(0.025, 0.50, 0.975))
# 
# b1_quant_pre <- data.frame(t(b1_quant_pre))
# names(b1_quant_pre) <- c("Q2.5", "Q50", "Q97.5")

# Combine summary statistics of posterior simulation draws
# b1_df_pre_cred <- data.frame(variables = "ATT before project",
#                              post_mean = b1_mean_pre,
#                              post_sd = b1_sd_pre,
#                              b1_quant_pre[2], 
#                              b1_quant_pre[1],
#                              b1_quant_pre[3])
#

##
# After
##
# b1_sims_after <- as.matrix(reg_ps_pos, 
#                      pars = "indicator_muni_ot")
#   
# Compute mean, SD, median, and 95% credible interval of treatment

# Posterior mean and SD of treatment
# b1_mean_after <- mean(b1_sims_after) # posterior mean
# b1_sd_after <- sd(b1_sims_after)       # posterior SD
# 
# # Posterior median and 95% credible interval
# b1_quant_after <- quantile(b1_sims_after,   probs = c(0.025, 0.50, 0.975))
# 
# b1_quant_after <- data.frame(t(b1_quant_after))
# names(b1_quant_after) <- c("Q2.5", "Q50", "Q97.5")

# Combine summary statistics of posterior simulation draws
# b1_df_after_cred <- data.frame(variables = "ATT After project",
#                              post_mean = b1_mean_after,
#                              post_sd = b1_sd_after,
#                              b1_quant_after[2], 
#                              b1_quant_after[1],
#                              b1_quant_after[3])
# b1_df <- bind_rows(b1_df_pre_cred, b1_df_after_cred)
```

@@

# b1_df %>% gt() %>%
#   tab_header(
#     title = "Effect of local OSB social monitoring on construction delivery rates",
#     subtitle = "Posterior probabilities") %>%
#   cols_label(
#     variables = "Variables",
#     post_mean = "Mean",
#     post_sd = "Sd",
#     Q50 = "Median",
#     Q2.5 = "2.5% CI",
#     Q97.5 = "97.5% CI"
#   ) %>%
#   fmt_number(
#     columns = c(post_mean, post_sd, Q50, Q2.5, Q97.5 ),
#     decimals = 3,
#     use_seps = FALSE
#   ) %>%
#   tab_source_note(
#     source_note = "452 observations for the pre-treatment period and 320 observations for the post-treatment period, resulting from the matching procedure, and encompassing municipalities in the same states as municipalities of Obra Transparente"
#   ) %>%
#   tab_options(., container.width = 500, container.height =     500)
